Bird beak's elaboration and exploration

### 2021-09-10 Analysis/02-MCMCglmm_mini_chains.Rmd
Update 02-MCMCglmm_mini_chains.Rmd

```{r, get_model_parameters, eval = FALSE}
## Load the computed models
param_chains <- list()
for(i in 1:3) {
    load(paste0("../Data/Cluster/allbirds_ 8748t_8Dshapespace_31levels/param_chains/params_shapespace_8D_31levels_20k_chain", i, ".rda"))
    param_chains[[i]] <- params_shapespace_8D_31levels[[1]]
}
## Extract the parameters from the parameter chains
est_params <- extract.parameters(param_chains)
```

@@

## Set up the mini-chains models
shapespace_8748t_8D_32level <- make.mini.chains(
                                data         = shapespace,
                                dimensions   = selected_dim,
                                tree         = consensus_tree,
                                trait.family = "gaussian",
                                randoms      = c("global", "level1", "level2"),
                                residuals    = "global",
                                priors       = est_params$priors,
                                verbose      = TRUE,
                                parameters   = list(
                                    nitt   = est_params$burnin + thin * samples,
                                    thin   = thin,
                                    burnin = est_params$burnin))
## Save the mini.chains
save(shapespace_8748t_8D_32level, file = "shapespace_8748t_8D_32level.mini.chains")
```

>>>>

```{r, get_model_parameters, eval = FALSE}
## Load the computed models
param_chains <- list()
for(i in 1:3) {
    load(paste0("../Data/Cluster/allbirds_8748t_8Dshapespace_31levels/param_chains/params_shapespace_8D_31levels_20k_chain", i, ".rda"))
    param_chains[[i]] <- params_shapespace_8D_31levels[[1]]
}
## Extract the parameters from the parameter chains
est_params <- extract.parameters(param_chains)
```

@@

## Set up the mini-chains models
shapespace_8748t_8D_32level <- make.mini.chains(
                                data         = shapespace,
                                dimensions   = selected_dim,
                                tree         = trees_list[sample(1:1000, 20)],
                                trait.family = "gaussian",
                                randoms      = c("global", "level1", "level2"),
                                residuals    = "global",
                                priors       = est_params$priors,
                                verbose      = TRUE,
                                parameters   = list(
                                    nitt   = est_params$burnin + thin * samples,
                                    thin   = thin,
                                    burnin = est_params$burnin))
## Save the mini.chains
save(shapespace_8748t_8D_32level, file = "../Data/Cluster/allbirds_8748t_8Dshapespace_31levels/shapespace_8748t_8D_32level.mini.chains")
```
